Prag Bat

### 2021-05-26 analysis/reliability.Rmd
update to run study

data <- bind_rows(
data_r1 <- read_csv("../data/data_r1.csv")%>%mutate(id = paste(id,"r1",sep = "_")) ,
data_r2 <- read_csv("../data/data_r2.csv")%>%mutate(id = paste(id,"r2",sep = "_"))
)%>%
  filter(task !="training")

>>>>

data <- bind_rows(
data_r1 <- read_csv("../data/data_r1.csv")%>%mutate(id = paste(id,"r1",sep = "_")) ,
data_r2 <- read_csv("../data/data_r2.csv")%>%mutate(id = paste(id,"r2",sep = "_"))
)%>%
  filter(task !="training")%>%
  mutate(item = ifelse(task == "mutual_exclusivity" & item == "t22", "carrot", item),
         item = ifelse(task == "mutual_exclusivity" & item == "t37", "duck", item),
         item = ifelse(task == "mutual_exclusivity" & item == "t24", "duck", item))

data %>%
  filter(task == "mutual_exclusivity")%>%
  group_by(subage,item)%>%
  summarise(mean= mean(correct))
```
